---
title: "Option A: Strings and functional programming in R"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is my deliverable for assignment B-4. My tasks are to:

0. Submit a Tidy repository on github (25 points)
1. Complete Exercise 1 (37.5 points)
2. Complete Exercise 3 (37.5 points)

Before starting on this task, I first need to download and load the appropriate packages

```{r}
#packages needed
library(janeaustenr)
library(ggplot2)
library(plotly)
library(hpackedbubble)
library(webshot) #this package is needed with hpackadbubble
library(tidyverse)
library(qdap)#this package needs rJava so make sure you have installed this package
library(tm)
library(kableExtra)
library(MASS)
```

## Exercise 1 (37.5 points)

For this exercises I need to use the  janeaustenr package and make a plot with the most common words in the book removing “stop words” of your choosing (words like “the”, “a”, etc.)

For this exercise I decided to look at all the books and not just one.

I then mapped through the books using the freq_terms function from the [qdap](https://github.com/trinker/qdap) package. This making the code more efficient and clean.

I generated an interactive table and a bubble plot for the user to have a look at all the common words,removing all stopwords using the [tm](https://www.rdocumentation.org/packages/tm/versions/0.7-8) package that have at least 5 characters and appear 10 times in each book.

The table and bubble plot are interactive. The bubble plot groups the words per book and these appear in circles/bubbles and the different colors reprsent the different books.

```{r}
#load the books from the janeaustenrpackage and create an object know as df
df <- janeaustenr::austen_books() %>% 
  nest(data = text) %>% #nest data to allow for looping
  mutate(freq = map(data, 
                    ~ qdap::freq_terms(.x$text, 10,
                      at.least = 5, tm::stopwords("english")))) # mapping the text list through the freq_terms function, looking for words that were 5 characters that was used at least 10 times that did not include "English" stopwords, these were removed tm package

df1 <- df %>%
  dplyr::select(-data) %>% # removing column
  unnest(freq)

#interactive table using kableExtra package
kbl1 <- kbl(df1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))%>%
  scroll_box(width = "500px", height = "500px")

kbl1
```

```{r}
## this was from the hpackedbubble package using the dataframe from the first section to create an interactive display of results
bubplot <- hpackedbubble(df1$book, df1$WORD, df1$FREQ,
              title = "Common words in Jane Austens books",
              pointFormat = "<b>{point.name}:</b> {point.y} words<sub>",
              dataLabelsFilter = 100,
              packedbubbleMinSize = "10%",
              packedbubbleMaxSize = "300%",
              theme = "sunset",
              packedbubbleZMin = 0,
              packedbubbleZmax = 3000, split = 1,
              gravitational = 0.02,
              parentNodeLimit = 1,
              dragBetweenSeries = 0,
              width = "100%")

bubplot
```
The code chunk below gives a longer way of doing the same analysis if the use of stringr needed to be demonstrated.It is heavier and does slow R when running.However produces similar results

```{r}

#tidy_books <- austen_books() %>%
#  group_by(book) %>%
#  mutate(
#    linenumber = row_number(),
#    chapter = cumsum(str_detect(text, 
#                               regex("^chapter [\\divxlc]", 
#                                      ignore_case = TRUE)))) %>%
#  ungroup() %>%
#  unnest_tokens(word, text)

#tidy_books %>%
#  filter(str_count(word) >= 5) %>%  # similar to the at.least = 5
#  anti_join(stop_words) %>%   # similar to tm::stopwords()
#  group_by(book) %>% 
#  count(word) %>% 
 # arrange(book, desc(n))

```

## Exercise 3  (37.5 points)

For this exercise,I was evaluating model a that’s fit separately for each group in the Boston data set found in the MASS package. 

The question I I had in mind is:

1.To fit a simple linear regression model `crim` against the other predictors in the data set

From the results below some of the key take aways are:
 -varaibles are predictors for crime in Boston apart from char variable, according to analysis.

```{r}
#creating a new list column with the column model added to the tibble 
bos <- tibble(var = names(Boston)[-1]) %>% 
  mutate(lm = map(var, ~lm(paste("crim ~",.), data = Boston) %>% tidy)) %>%
  unnest(lm) 

#interactive tablle to show the results from the liner regression

bos1<- kbl(bos) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))%>%
  scroll_box(width = "500px", height = "500px")

bos1
```


```{r}
# I created a plot because the assignment requested for one however, I don't think it makes sense as all the other indicators show that they can predict crime according to the anlaysis

p1 <- ggplot(bos,aes(statistic,estimate, color = term))+
  geom_point()+
  theme_classic()


ggplotly(p1)


#plot(bos)
# this did not make sense.
```

